What defines big team science?

### 2025-07-15 appendix.Rmd
fixing author typo
updated formatting
changes to resubmit
updating manuscript

---
appendix: "appendix.Rmd"
---

# Supplemental Materials

## RQ1: Publisher Information.

```{r setup-appendix}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(ggplot2)
library(ggwordcloud)
library(figpatch)
library(RColorBrewer)
library(latex2exp)
library(ggridges)
```

**Number of Journals**.

Table \@ref(tab:tab-snip) indicates the SNIP values for BTS publications, while Table \@ref(tab:tab-snip-all). The results from these tables indicate that impact values are slightly higher for BTS publications, while the overall median, minimum, and maximum are the same for each grouping.

```{r tab-snip, results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)), 
  caption = "Big-Team Science SNIP Values")
```

```{r tab-snip-all, results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)),
  caption = "All Journal Articles SNIP Values")
```

## RQ2: Publication Information.

**Keywords**. Figure \@ref(fig:fig-keywords) indicates the most common keywords present for the BTS publications by subject area. The keywords were tokenized into single tokens. Keywords were then lowercased, and all stop words (for example, the, an, of, into, for) were removed. Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.

```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RERUN THIS ###
# health
health_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/health_key.png", dpi = 300, width = 8,
       height = 4, units = "in")

# physical
physical_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Physical Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/physical_key.png", dpi = 300, width = 8,
       height = 4, units = "in")

# life
life_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Life Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/life_key.png", dpi = 300, width = 8,
       height = 4, units = "in")

# social 
social_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Social Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/social_key.png", dpi = 300, width = 8,
       height = 4, units = "in")
```

```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas."}
health_key <- fig("figure/health_key.png")
physical_key <- fig("figure/physical_key.png") 
life_key <- fig("figure/life_key.png") 
social_key <- fig("figure/social_key.png")

health_key + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
physical_key + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
life_key + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
social_key + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)

ggsave("figure/figure_app_1.png")
```

## RQ3: Authors

**Institution**.

Institution was normalized by taking the total number of unique institutions and dividing by the total number of institution listings. The patterns are similar for each decade in that papers are often either half unique institutions or mostly unique institutions overall as show in Figure \@ref(fig:fig-inst).

```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades."}
DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100

graph_data_inst <- DF$inst_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  mutate(Decade = as.factor(Decade))

picture <- ggplot(graph_data_inst,
                  aes(y = Decade, x = normalized)) + 
  geom_density_ridges2() + 
  theme_classic() + 
  facet_wrap(~SubjectArea) + 
  xlab("Percent of Unique Affiliations") + 
  ylab("Decade") +
  coord_cartesian(xlim = c(0, 100))

suppressWarnings(print(picture))

ggsave("figure/figure_app_2.png")
```

***Education***. As noted in our pre-registration, we would only present this variable if we could obtain at least 50% information on the authors who publish in big team science papers. `r apa_num(24228428/25282810*100)`% of the data was not available.

***Types of Publications***.

Types of publications are presented in Figure \@ref(fig:fig-pub-types). The patterns of publications are roughly similar for big team science authors and all authors. It appears that porportionally, big team members are more likely to post preprints in comparison to all authors.

```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
pub_levels <- c("ab", "ar", "ip", "bk", "bz", "ch", "cp", 
                "cr", "dp", "ed", "er", "le", "no", "pp", 
                "pr", "rp", "re", "sh", "tb")
pub_labels <- c("Abstract", "Article", "In Press", "Book", "Business", "Book Chapter", "Conference Paper", 
                "Conference Report", "Data Paper", "Editorial", "Erratum", "Letter", "Note", 
                "Preprint", "Press Release", "Report", "Review", "Survey", "Retracted")

pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "All Papers")) %>% 
    filter(!is.na(publication_type)) %>% 
  filter(publication_type != "cb") %>% 
  mutate(publication_type = factor(publication_type, 
                                   levels = pub_levels,
                                   labels = pub_labels)) %>% 
  mutate(binned_count = ifelse(
    count < 10000, "< 10,000", ifelse(
      count > 10000 & count < 100000, "10,000 - 99,999", ifelse(
        count > 100000 & count < 1000000, "100,000 - 999,999", ifelse(
          count > 1000000 & count < 10000000, "1,000,000 - 9,999,999", "> 10,000,000"
        )
      )
    )
  )) %>% 
  mutate(binned_count = factor(binned_count,
                               levels = c("< 10,000", 
                                          "10,000 - 99,999",
                                          "100,000 - 999,999", 
                                          "1,000,000 - 9,999,999",
                                          "> 10,000,000")))

ggplot(pub_types, aes(area = count, fill = binned_count,
               label = publication_type)) +
  geom_treemap() +
  facet_wrap(~type) + 
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_brewer(name = "Sample Size", palette = "Spectral") +
  theme_classic()

ggsave("figure/figure_app_3.png")
# can probably figure out how to combine these feasibly to make it readable
# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.
```

>>>>

# Supplemental Material

We have included several supplemental tables and figures for visualization of results discussed in the manuscript.

```{r rate-estimates-fig, include = TRUE, fig.cap = "Exponential growth rate estimates with 95% confidence intervals.", out.width='100%'}
knitr::include_graphics("figure/figure_3_growth.png")
```

```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications. The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right. Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.", out.width='100%'}
knitr::include_graphics("figure/figure_6_map.png")
```

```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year. Larger dots indicate more papers and authors represented in the calculation of effect size.", out.width='100%'}
knitr::include_graphics("figure/figure_8_author_effect_gpe.png")
```

```{r big-teams-table, results = 'asis'}
big_teams_papers <- 968765
big_teams_authors <- 4541369

apa_table(DF$paper_stats %>% 
        arrange(Statistic), 
        caption = "Number of Authors and Papers by Subject Area",
        note = "Papers can be classified into multiple categories.", 
        align = c("l", rep("c", 5)), 
        digits = 0)
```

### 2025-07-15 manuscript_definition.Rmd
updating manuscript

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

# Supplement

We have included several supplemental tables and figures for visualization of results discussed in the manuscript.

```{r rate-estimates-fig, include = TRUE, fig.cap = "Exponential growth rate estimates with 95% confidence intervals.", out.width='100%'}
knitr::include_graphics("figure/figure_3_growth.png")
```

```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications. The mosaic plot is grouped by UN subregion with the largest number of publications starting on the bottom left and smallest on the top right. Therefore, North America represents the largest number of authors within BTS (i.e., bottom right, then separated into the geopolitical areas within that subregion), followed by Eastern Europe (top left), and so on.", out.width='100%'}
knitr::include_graphics("figure/figure_6_map.png")
```

```{r fig-effect-gpe, include = TRUE, fig.cap = "Effect size of the differences in representation for UN Regions for author affiliations in big-team science papers by year. Larger dots indicate more papers and authors represented in the calculation of effect size.", out.width='100%'}
knitr::include_graphics("figure/figure_8_author_effect_gpe.png")
```

```{r big-teams-table, results = 'asis'}
big_teams_papers <- 968765
big_teams_authors <- 4541369

apa_table(DF$paper_stats %>% 
        arrange(Statistic), 
        caption = "Number of Authors and Papers by Subject Area",
        note = "Papers can be classified into multiple categories.", 
        align = c("l", rep("c", 5)), 
        digits = 0)
```

>>>>

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
appendix          : "appendix.Rmd"
---

@@

# (APPENDIX) Appendix {.unnumbered}

```{r child = "appendix.Rmd"}
```
